---
title: "Untitled"
author: "Shane Dewees"
date: "2023-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(raster)
library(here)
```

Read in in the grazing and parcel data:
 - create a name to store each data file as in the local environment (i.e. grazing_data)
 - remember that <- tells R to store to a name
 - use the st_read and here functions.
 - inside here, put each folder and then the shapefile inside quotes. 
 
 -inside mutate create a column called grazed_status and then have each row be equal to grazed or ungrazed. 
 - Then use the select function to only keep the grazed_status and geometry columns

```{r}
______ <- st_read(here()) %>% #read in grazed data here remember the "%>%" tells R to run the next line of code applied to the line you just wrote. 
  mutate() %>% 
  dplyr::select() %>% 
  st_as_sf() #sometimes data manupilation confuses R as to if this is spatial data, so this function just reminds R we are still working with spatial data. 

______ <-  # Repeat above for parcel data
  %>% 
  st_zm() #end this chunk of code with this function to get rid of z data. 

parcel_no_Grazing <- st_difference() %>% #use st_difference function to get the parcel data that is not overlapped by the grazed data
   %>% #select grazed_status and geometry
   %>% #reset the grazed status to ungrazed (Hint: use mutate function)
  st_sf()

grazing_overlap <- st_intersection() %>% #now get the overlap between the two data frames
   %>%  # select grazed-status and geometry
   %>%  # reset the grazed status to grazed
  st_sf()

 # repeat above but to get the grazing data that is not overlapped by parcel data. 
  
all_data <- rbind() #combine the three data frames you just made

plot(all_data) #Check it out!
```



```{r}
grazing_data <- st_read(here("data", "sb_parcel_data", "grazing_parcel_subset.shp")) %>% 
mutate(grazed_status = "grazed")%>%
dplyr::select("grazed_status","geometry")%>% 
st_as_sf()

 

parcel_data <- st_read(here("data", "sb_parcel_data", "parcel_map_subset.shp"))%>%
mutate(grazed_status= "ungrazed")%>%
dplyr::select("grazed_status","geometry")%>% 
st_as_sf()%>% 
st_zm()
 
parcel_no_Grazing <- st_difference(parcel_data, grazing_data)%>%
dplyr::select("grazed_status","geometry")%>%
mutate(grazed_status="ungrazed")%>%
st_as_sf()

grazing_overlap <- st_intersection(parcel_data, grazing_data)%>%
dplyr::select("grazed_status","geometry")%>%
mutate(grazed_status="grazed")%>%
st_as_sf()

grazing_no_parcel <- st_difference(grazing_data, parcel_data)%>%
dplyr::select("grazed_status","geometry")%>%
mutate(grazed_status="grazed")%>%
st_as_sf()

all_data <- rbind(parcel_no_Grazing, grazing_no_parcel, grazing_overlap)
plot(all_data)

```

```{r}
landsat_list <- list.files(path = here("data", "LC08_L2SP_042036_20221105_20221115_02_T1"), pattern = '.TIF$', all.files = TRUE)

landsat <- raster::stack(here("data", "LC08_L2SP_042036_20221105_20221115_02_T1", landsat_list))
```

