---
title: "Untitled"
author: "Shane Dewees"
date: "2023-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(raster)
library(here)
```

Read in in the grazing and parcel data:
 - create a name to store each data file as in the local environment (i.e. grazing_data)
 - remember that <- tells R to store to a name
 - use the st_read and here functions.
 - inside here, put each folder and then the shapefile inside quotes. 
 
 -inside mutate create a column called grazed_status and then have each row be equal to grazed or ungrazed. 
 - Then use the select function to only keep the grazed_status and geometry columns

```{r}
_____ <- st_read(here()) %>% #read in grazed data here remember the "%>%" tells R to run the next line of code applied to the line you just wrote. 
  mutate() %>% 
  dplyr::select() %>% 
  st_as_sf() #sometimes data manupilation confuses R as to if this is spatial data, so this function just reminds R we are still working with spatial data. 

______ <-  # Repeat above for parcel data
  %>% 
  st_zm() #end this chunk of code with this function to get rid of z data. 

parcel_no_Grazing <- st_difference() %>% #use st_difference function to get the parcel data that is not overlapped by the grazed data
   %>% #select grazed_status and geometry
   %>% #reset the grazed status to ungrazed (Hint: use mutate function)
  st_sf()

grazing_overlap <- st_intersection() %>% #now get the overlap between the two data frames
   %>%  # select grazed-status and geometry
   %>%  # reset the grazed status to grazed
  st_sf()

 # repeat above but to get the grazing data that is not overlapped by parcel data. 
  
all_data <- rbind() #combine the three data frames you just made

plot(all_data) #Check it out!
```


